---
title: "E-Commerce"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(readxl)
library(yaml)
library(scales)
library(ggvis)

```

# MainDashBoard

Column {data-width=600, .tabset}
--------------------------------------------------

### Ship Mode

```{r}
Modeof_Shipment<- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls", 
                              sheet = "Mode of shipment")
View(Modeof_Shipment)

ShipMode<-Modeof_Shipment$`Ship mode`
Total<-Modeof_Shipment$Total
b<-ggplot(Modeof_Shipment)+
  geom_bar(aes(x=ShipMode, y=Total),fill= 'blue', stat = 'identity')+
  ggtitle("Shipment Mode")+
  theme(axis.text.x = element_text(angle = 90,vjust = 0.5,hjust = 1))
Chart1<-ggplotly(b)
Chart1


```

### Product Wise Sales


```{r}

Productwise<- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls", 
                          sheet = "Product wise sales")

prodcutlist <- data.frame(Products=c(Productwise$`sub-category`), 
                           Total = c(Productwise$Total))
b1<-ggplot(prodcutlist, aes(x=Products,y = Total)) +geom_bar(fill="blue",stat = "identity")+
  expand_limits(x = c(0, NA), y = c(0, NA))+
  scale_y_continuous(labels = unit_format(unit = "M", scale = 1e-6))+
                       theme(axis.text.x = element_text(angle = 90,vjust = 0.5,hjust = 1))
  
Chart2<-ggplotly(b1)
Chart2

```

### Average Sales

```{r}

Sample_Superstore <- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls")

gauge(round(mean(Sample_Superstore$Sales),
            digits = 2),
      min = 0,
      max = 300,
      gaugeSectors(danger = c(0,100),
                   warning = c(100,150),
                   success =   c(150,250),
                 colors =c("blue","yellow","red")))

```

Column {data-width=500, .tabset}
-----------------------------------------------

### Region Wise Sales

```{r}


Region <- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls", 
                     sheet = "Region")


                     
data <- Region[,c('Region', 'Total')]
pie <- plot_ly(data, labels = ~Region, values = ~Total,fill=Region, type = 'pie')
pie <- pie %>% layout(title = 'Regional Wise Sales',
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

pie


```

### Year Wise Sales

```{r}

Sample_Superstore <- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls", 
                                sheet = "Year wise sales")

Year<-Sample_Superstore$`Order year`
Sales<-Sample_Superstore$`Total Sales`

b<-ggplot(data,aes(x = Year, y = Sales))+
  ggtitle("YEARWISE Sales")+
  geom_line()+geom_point()+
  
  scale_x_continuous(
    breaks = seq(from = 2014, to = 2017, by = 1),
    limits = c(2014, 2017)
  )
b1<-ggplotly(b)
b1
  

```








# Map

Column {data-width=500, .tabset}
--------------------------------------------------

```{r}
library(readxl)
Sample_Superstore <- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls", 
    sheet = "Super store")
Data<-Sample_Superstore%>%
group_by(State)%>%
  summarise(Sales)
  highchart()%>%
    hc_title(text="State Wise Sales")%>%
    hc_subtitle("Source:E-Commerce")%>%
    hc_add_series_map(usgeojson,Data,
                      names="State",
                      value = "Sales",
                      joinBy = c("woename","State"))%>%
    hc_mapNavigation(enabled=T)
```

Data Table
========================================

Column {data-width=500, .tabset}
--------------------------------------------------

```{r}
library(readxl)
Data <- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls", 
    sheet = "Super store")
datatable(Data,
          caption = "E-Commerce Data",
          rownames = T,
          filter = "top",
          options = list(pageLength=25))


```


# Sales Report

Column {data-width=500, .tabset}
--------------------------------------------------

```{r}

Data <- read_excel("C:/Users/rejee/OneDrive/Desktop/Msc_Assignments/Data visualisation Essay Writing; Dashboard Implementation/Sample - Superstore.xls", 
    sheet = "Super store")
rpivotTable(Data,
            aggregatorName = "Maximum",
            cols = "Region",
            rows = "State",
            rendererName = "Bar Chart"
            )
```

Summary Reports {data-orientaion=columns}
============================================

Column {data width=100}
--------------------------
### Total number of orders

```{r}
valueBox(length(Data$Sales),
         icon = "fa-user")

```

### Total Sales

```{r}
valueBox(sum(Data$Sales),
         icon ="fa-user")
```

### Average Sales by order

```{r}
valueBox(mean(Data$Sales),
         icon = "fa-user")
```

### Total Discount

```{r}
valueBox(sum(Data$Discount),
         icon = "fa-user")
```

Column
--------------

Report

* Total number of orders =`r length(Data$Sales)`
* Total Sales =`r sum(Data$Sales)`
* Average Sales by Order = `r mean(Data$Sales)`
* Total Discount = `r sum(Data$Discount)`





